\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex
added def of vertice-induced subgraph

The graph processing algorithm is executed locally by a node (line 10 of \cref{fig:deps-set-algo3}). It must compute the value of $\opn{c-struct}\left( g_p \right)$, as defined in \cref{lindef}.
Its key property is \cref{lemma:graph}. 
We assume that processes initially agree, for each set of commands $\mathcal{D}$, on a total order $<_{\mathcal{D}}$ on $\mathcal{D}$.
In practice, if commands are attached a unique identifier among a totally ordered set, $<_{\mathcal{D}}$ can be the restriction of this total order to $\mathcal{D}$.

@@

Define the intersection of two graphs such that $V\left( g_1 \cap g_2 \right)=V\left( g_1 \right)\cap V\left( g_2 \right)$ and $E\left( g_1 \cap g_2 \right)= E\left( g_1 \right)\cap E\left( g_2 \right)$, and define their union such that $V\left( g_1 \cup g_2 \right)=V\left( g_1 \right)\cup V\left( g_2 \right)$ and $E\left( g_1 \cup g_2 \right)= E\left( g_1 \right)\cup E\left( g_2 \right)$.
Define two graphs $g_1$ and $g_2$ as being \emph{compatible} iff $g_1 \cap g_2$ is a vertex-induced subgraph of $g_1 \cup g_2$.

>>>>

The graph processing algorithm is executed locally by a process (line 10 of \cref{fig:deps-set-algo3}). It must compute the value of $\opn{c-struct}\left( g_p \right)$, as defined in \cref{lindef}.
Its key property is \cref{lemma:graph}. 
We assume that processes initially agree, for each set of commands $\mathcal{D}$, on a total order $<_{\mathcal{D}}$ on $\mathcal{D}$.
In practice, if commands are attached a unique identifier among a totally ordered set, $<_{\mathcal{D}}$ can be the restriction of this total order to $\mathcal{D}$.

@@

Define graph intersection such that $V\left( g_1 \cap g_2 \right)=V\left( g_1 \right)\cap V\left( g_2 \right)$ and $E\left( g_1 \cap g_2 \right)= E\left( g_1 \right)\cap E\left( g_2 \right)$, and graph union such that $V\left( g_1 \cup g_2 \right)=V\left( g_1 \right)\cup V\left( g_2 \right)$ and $E\left( g_1 \cup g_2 \right)= E\left( g_1 \right)\cup E\left( g_2 \right)$.
Define two graphs $g_1$ and $g_2$ as being \emph{compatible} iff $g_1 \cap g_2$ is a vertex-induced subgraph of $g_1 \cup g_2$ ($g$ is a vertex-induced subgraph of $g'$ iff $V\left( g \right)\subseteq V\left( g' \right)$ and if both endpoints of $e\in E\left( g' \right)$ are in $V\left( g \right)$, then $e\in E\left( g \right)$).
